\vspace{-1in}Identity signaling model progress

### 2020-02-19 reports/Progress-2-19.tex
finished coevolution experiment, analysis, and writeup

I systematically varied $r/R$ by setting $R=0.5$ and varied 
$r \in \{0.0, 0.05, 0.1, \ldots, 0.45\}$ to get $r/R \in \{0.0, 0.1, \ldots, 0.9\}$.
I varied homophily similartly to $r$, $w \in \{0.0, 0.5, \ldots, 0.45\}$. Note
that both $r$ and $w$ are bounded above by 0.5.

\begin{figure}[H]
  \centering
  \includegraphics[width=0.8\textwidth]{Figures/exampleMidrangeSeries.pdf}
  \caption{Timeseries of nine combinations of $r/R$ and $w$.}
  \label{fig:receptivityHomophilySeries}
\end{figure}

\begin{figure}[H]
  \centering
\includegraphics[width=0.8\textwidth]{Figures/covertDensityVsReceptivityHomophily.pdf}
  \caption{Density of covert signalers at $t=100$, final timestep recorded
    in this preliminary experiment.}
  \label{fig:receptivityHomophilyHeatmap}
\end{figure}

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=0.8\textwidth]{Figures/dislikingHomophilySeries.pdf}
  \caption{Timeseries of nine combinations of $d=\delta$ and $w$.}
  \label{fig:dislikingHomophilySeries}
\end{figure}

\begin{figure}[H]
  \centering
\includegraphics[width=0.8\textwidth]{Figures/covertDensityVsDislikingHomophily.pdf}
  \caption{Density of covert signalers at $t=100$, final timestep recorded
    in this preliminary experiment.}
  \label{fig:dislikingHomophilyHeatmap}
\end{figure}

>>>>

I systematically varied $r/R$ by setting $R=0.5$ and varied 
$r \in \{0.0, 0.05, 0.1, \ldots, 0.45\}$ to get $r/R \in \{0.0, 0.1, \ldots, 0.9\}$.
I varied homophily identically to $r$, $w \in \{0.0, 0.5, \ldots, 0.45\}$. Note
that both $r$ and $w$ are bounded above by 0.5.

\begin{figure}[H]

  \centering
  \begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{Figures/receptivityHomophilyCovertSeries.pdf}
    \caption{Density of covert signalers.}
  \end{subfigure}
  \begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{Figures/receptivityHomophilyChurlishSeries.pdf}
    \caption{Density of churlish receivers.}
  \end{subfigure}

  \caption{Timeseries of density of covert signalers and churlish receivers
    for nine combinations of $r$ and $w$. Receptivity of
    overt signals is $R=0.5$.}
  \label{fig:dislikingHomophilySeries}
\end{figure}

\begin{figure}[H]
  \centering
  \begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{Figures/covertDensityVsReceptivityHomophilyCoevo.pdf}
    \caption{Density of covert signalers.}
  \end{subfigure}
  \begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{Figures/churlishDensityVsReceptivityHomophilyCoevo.pdf}
    \caption{Density of churlish receivers.}
  \end{subfigure}

  \caption{Density of covert signalers and churlish receivers at $t=200$, 
    final timestep recorded in this preliminary experiment. Receptivity of
    overt signals is $R=0.5$.}
  \label{fig:dislikingHomophilyHeatmap}
\end{figure}

@@

\begin{figure}[H]

  \centering
  \begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{Figures/dislikingHomophilyCovertSeries.pdf}
    \caption{Density of covert signalers.}
  \end{subfigure}
  \begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{Figures/dislikingHomophilyChurlishSeries.pdf}
    \caption{Density of churlish receivers.}
  \end{subfigure}

  \caption{Timeseries of density of covert signalers and churlish receivers
    for nine combinations of $d=\delta$ and $w$.}
  \label{fig:dislikingHomophilySeries}
\end{figure}

\begin{figure}[H]
  \centering
  \begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{Figures/covertDensityVsDislikingHomophilyCoevo.pdf}
    \caption{Density of covert signalers.}
  \end{subfigure}
  \begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{Figures/churlishDensityVsDislikingHomophilyCoevo.pdf}
    \caption{Density of churlish receivers.}
  \end{subfigure}

  \caption{Density of covert signalers and churlish receivers at $t=200$, 
    final timestep recorded in this preliminary experiment.}
  \label{fig:dislikingHomophilyHeatmap}
\end{figure}
